---
title: "COMPSCIX 415.2 Homework 1"
author: "Nnenna Ibeanusi"
date: "6/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
My Github repository for my assignments can be found at this URL: https://github.com/nibeanusi/compscix-415-2-assignments
```{r}
library(mdsr)
library(tidyverse)

data("WorldCities")

?WorldCities

glimpse(WorldCities) #look at the data
```

There are 23,018 observations and 10 variables in the World Cities dataset.

```{r}
WorldCities <- head(WorldCities, 200)  # 200 rows

country_col <- WorldCities$country

unique(country_col)

```

country_col <- select(WorldCities, country)
country_col <-WorldCities%>% select(country)

?select #select is a function

```The %>% is a pipe operator. It works by plugging in WorldCities as the first argument in the select function - it is equivalent to select(WorldCities, country). ```

```{r}
WorldCities %>% select(region) %>% head(5)
```

Answers Question 2
```{r}
region_column<-WorldCities %>%select(region) 
unique(region_column) 
```

Answer Question 3
WorldCities%>%select(country)%>%unique()

WorldCities %>% ggplot(aes(x = population)) + geom_histogram()

WorldCities %>% ggplot(aes(x = population)) + geom_histogram() + xlab('City Population')
 
Answer Question 4
WorldCities %>% ggplot(aes(x = population)) + geom_histogram() + xlab('City Population in Milions') +ylab('Frequency')

WorldCities %>% ggplot(aes(x = population)) + geom_histogram() + xlab('City Population in Milions') +ylab('Frequency') + ggtitle('Frequency Distribution of City Population')

WorldCities %>% ggplot(aes(x = population)) + geom_histogram() + xlab('City Population in Milions') +ylab('Frequency') + ggtitle('Frequency Distribution of City Population') + theme_bw()