---
title: "ggplot2_class2"
author: "Nnenna Ibeanusi"
date: "6/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## get the library specific to what we are doing
```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(ggplot2)
library(mdsr)
```
## get information for the dataset that we are using
```{R}
?mpg
```

## get information for plot function
```{R}
?plot
```

```{r}
data(mpg)
```

###
```{R}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, size = class))
```


###
```{R}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, shape = class))
```
###
```{R}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = class))
```

###
```{R}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, alpha = class))
```

###
```{R}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = 'blue', alpha = .5)
```

###
```{R}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))
```

###geo_smooth, created a smooth line through the points
```{R}
ggplot(data = mpg) + 
  geom_smooth(mapping = aes(x = displ, y = hwy))
```

###
```{R}
ggplot(data = mpg) + 
  geom_smooth(mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping = aes(x = displ, y = hwy))
```

###use the same mapping that you already define in the ggplot, instead of in the geo_smooth and geo_point
```{R}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth() +
  geom_point()
```

###
```{R}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth() +
  geom_point(mapping = aes(color = drv))
```

###grouping, creates a different line for each group
```{R}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(mapping = aes(group = drv)) +
  geom_point(mapping = aes(color = drv))
```

###load the diamonds dqtaset and look at the first couple of rows in the dataset
```{R}
data("diamonds")
head(diamonds)
```

###
```{R}
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = cut))
```

###
```{R}
ggplot(data = diamonds) +
  stat_count(mapping = aes(x = cut))
```

###This does not work
###```{R}
###ggplot(data = diamonds) +
###stat_prop(mapping = aes(x = cut))
###```

###count variable and dividing by the sum of count
```{R}
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = cut, y = ..count../sum(..count..)))
```

###
```{R}
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = cut, y = ..count../sum(..count..)))
```

###
```{R}
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = cut, y = ..count../sum(..count..))) + 
  xlab('Cut of diamond')
```

###
```{R}
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = cut, y = ..count../sum(..count..))) +
  xlab('Cut of diamond') +
  ylab('Proportion') +
  ggtitle('Prevalence of each cut of diamond')
```

###
```{R}
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = cut, y = ..count../sum(..count..))) +
  xlab('Cut of diamond') +
  ylab('Proportion') +
  ggtitle('Prevalence of each cut of diamond') +
  theme_dark()
```

###
```{R}

```

###
```{R}

```

###
```{R}

```

###
```{R}

```

###
```{R}

```

###
```{R}

```

###
```{R}

```

```{r}

```

